### 2014-12-31 paper_10_intro.tex
adding more papers

\subsubsection{SOFTWARE ANALYTICS}
What is software analytics?
See also \cite{Buse2010}.

@@

>>>>

\subsubsection{SOFTWARE ANALYTICS}
What is software analytics?

Some of the measurements focus specifically on the source code; analyzing the 
complexity, size, and coupling \cite{Tosi2012}.

Letier and Fitzgerald discuss how to choose the correct tools and techniques to analyze
software data \cite{Letier2013}.  A goal model is produced that matches the data analysis methods
with the goals of the software stakeholders.  Again, the method does not focus
on analysis of development of software.

@@

See also \cite{Buse2010}.

### 2014-12-31 paper_30_measure.tex
adding some capitol letters to the section headers
adding more papers

More information on the indicators can be found
in chapter 1 of \cite{parmenter2010}
as well as \cite{florac1999,kaplan1992,letier2013}.

@@

\subsection{Possible data points for Level of Effort}

>>>>

More information on the indicators can be found
in chapter 1 of \cite{parmenter2010}
as well as \cite{florac1999,kaplan1992}.

@@

\subsection{POSSIBLE DATA POINTS FOR LEVEL OF EFFORT}
